---
title: "Now"
page-layout: full
---

```{r}
#| echo: false
#| output: asis
#| warning: false
#| message: false

# Load Hardcover API functions
source("scripts/hardcover.R")

# Load config (create _hardcover_config.R from the example file)
if (file.exists("_hardcover_config.R")) {
  source("_hardcover_config.R")

  # Fetch currently reading books
  tryCatch({
    books <- get_currently_reading(HARDCOVER_API_TOKEN, HARDCOVER_USER_ID)
    cat("") # Placeholder for inline display below
  }, error = function(e) {
    cat("") # Silent fail, will show placeholder text
  })
} else {
  cat("") # No config file, show placeholder
}
```

# What I'm Doing Now

```{r}
#| echo: false
#| output: asis
#| warning: false
#| message: false

source("scripts/last_updated.R")

cat(sprintf("*Last updated: %s*\n", last_updated("now.qmd")))
```

This is a [now page](https://nownownow.com/about), inspired by Derek Sivers, describing what I'm currently focused on.

## Current Focus

### Research

Postdoctoral Fellow at the Genetic and Molecular Epidemiology Group, CNIO, working on pancreatic and bladder cancer.

### Learning

- Máster de Formación Permanente en Salud Pública (UNED / ENS-ISCIII).
- PG Certificate in Public Health (LSHTM).
- Practical Epidemiology (EPM103), Statistical Methods in Epidemiology (EPM202) and Advanced Statistical Methods in Epidemiology (EPM304), taken standalone at LSHTM.
- Graduate Certificate in Theoretical Statistics and Probability (OU).
- Máster en Economía de la Salud y del Medicamento (UPF-BSM).
- Máster universitario de Análisis Económico (UOC).
- Máster en Análisis de las Desigualdades Sociales (UNED).

### Reading

```{r}
#| echo: false
#| output: asis
#| warning: false
#| message: false

# Display currently reading books
if (exists("books") && !is.null(books) && nrow(books) > 0) {
  knitr::asis_output(display_books_html(books))
} else {
  "- Reading: [Book Title] by [Author]\n"
}
```

## Recent Accomplishments

- Finished the Diploma de Experto Universitario en Métodos Avanzados de Estadística Aplicada (UNED), awaiting final results.
- Held a postdoctoral fellowship on the cancer genomics of vulvar and penile squamous cell carcinoma (Rakislova Lab, ISGlobal).
- Completed my PhD in Biomedicine at Universitat Pompeu Fabra — submitted September 2025, defended December 2025.

## Side Projects

**[etverse](https://etverse.github.io/)** — an R ecosystem for transparent causal inference.

- [`causatr`](https://github.com/etverse/causatr): causal effects estimation.
- [`negatr`](https://github.com/etverse/negatr): negative control analysis.
- [`matchatr`](https://github.com/etverse/matchatr): (matched) case-control and case-cohort study analysis.
- [`survatr`](https://github.com/etverse/survatr): survival analysis.

**Standalone R packages**

- [`forrest`](https://github.com/lorenzoFabbri/forrest): publication-ready forest plots.
- [`orcidtr`](https://github.com/lorenzoFabbri/orcidtr): ORCID public API client.

**Writing and tooling**

- [`bibaudit`](https://lorenzofabbri.github.io/bibaudit/): field-level verification of bibliographies against Crossref, DataCite, PubMed and Open Library.
- [`paper-template`](https://github.com/lorenzoFabbri/paper-template): a paper written in Markdown, built into a submission-ready DOCX, a Typst PDF and a journal bundle.
- [`manuscript-engine`](https://github.com/lorenzoFabbri/manuscript-engine): the Pandoc filters and build machinery behind `paper-template`, pinned into each paper as a submodule.

---

*Want to know what I was doing before? Check out the [blog](blog.qmd) for updates and reflections.*
