---
title: "Now"
page-layout: full
---

```{r}
#| echo: false
#| output: asis
#| warning: false
#| message: false

# Load Hardcover API functions
source("scripts/hardcover.R")

# Load configuration (create _hardcover_config.R from _hardcover_config_example.R)
if (file.exists("_hardcover_config.R")) {
  source("_hardcover_config.R")
  
  # Fetch currently reading books
  tryCatch({
    books <- get_currently_reading(HARDCOVER_API_TOKEN, HARDCOVER_USER_ID)
    cat("") # Placeholder for inline display below
  }, error = function(e) {
    cat("") # Silent fail, will show placeholder text
  })
} else {
  cat("") # No config file, show placeholder
}
```

# What I'm Doing Now

*Last updated: March 2026*

This is a [now page](https://nownownow.com/about), inspired by Derek Sivers, describing what I'm currently focused on.

## Current Focus

### Research

Preparing for my incoming postdoctoral fellowship at CNIO, focused on pancreatic and bladder cancer.

### Learning

- Postgraduate Certificate in Public Health (LSHTM).
- Graduate Certificate in Theoretical Statistics and Probability (OU).
- Master in Public Health (UNED).
- Master in Economic Analysis (UOC).

### Reading

```{r}
#| echo: false
#| output: asis
#| warning: false
#| message: false

# Display currently reading books
if (exists("books") && !is.null(books) && nrow(books) > 0) {
  knitr::asis_output(display_books_html(books))
} else {
  "- Reading: [Book Title] by [Author]\n"
}
```

## Recent Accomplishments

- Completed my PhD in Biomedicine at Universitat Pompeu Fabra (December 2025).

## Upcoming

- Starting postdoctoral fellowship at CNIO.

## Side Projects

- [`forrest`](https://github.com/lorenzoFabbri/forrest): R package for publication-ready forest plots.
- [`negatr`](https://github.com/etverse/negatr): R package for negative control analysis in epidemiology.
- [`orcidtr`](https://github.com/lorenzoFabbri/orcidtr): R package to access the ORCID public API.

---

*Want to know what I was doing before? Check out the [blog](blog.qmd) for updates and reflections.*
