---
title: "Now"
page-layout: full
---

```{r}
#| echo: false
#| output: asis
#| warning: false
#| message: false

# Load Hardcover API functions
source("_hardcover.R")

# Load configuration (create _hardcover_config.R from _hardcover_config_example.R)
if (file.exists("_hardcover_config.R")) {
  source("_hardcover_config.R")
  
  # Fetch currently reading books
  tryCatch({
    books <- get_currently_reading(HARDCOVER_API_TOKEN, HARDCOVER_USER_ID)
    cat("") # Placeholder for inline display below
  }, error = function(e) {
    cat("") # Silent fail, will show placeholder text
  })
} else {
  cat("") # No config file, show placeholder
}
```

# What I'm Doing Now

*Last updated: December 2025*

This is a [now page](https://nownownow.com/about), inspired by Derek Sivers, describing what I'm currently focused on.

## Current Focus

### Research

### Learning

- Deepening my knowledge of [topic/method]
- Learning [new skill/software]

```{r}
#| echo: false
#| output: asis
#| warning: false
#| message: false

# Display currently reading books
if (exists("books") && !is.null(books) && nrow(books) > 0) {
  cat("- **Currently Reading:**\n\n")
  knitr::asis_output(display_books_html(books))
} else {
  "- Reading: [Book Title] by [Author]\n"
}
```

## Recent Accomplishments

- Published new working paper (see [Research](research/index.qmd))

## Upcoming

## Side Projects

- Building [project description]

---

*Want to know what I was doing before? Check out the [blog](blog.qmd) for updates and reflections.*
